The Shape and <span style='color: #b70000'>Co</span><span style='color: #00AEF3'>lor</span> of Politics

### 2023-11-01 chapter_2/src/slides/color-book.qmd
updating the slides a bit more

---
title: "The Shape and Color of Politics"
author:
    - name: Damon C. Roberts [{{< fa brands orcid size=xs >}}](https://orcid.org/0000-0002-4360-3675)
format:
    simpledarkjs-revealjs:
        multiplex: true
        output-file: color-book.html
        slide-level: 5
        transition: none
bibliography: ../../../assets/candidate_support_chapter_references.bib
execute:
    echo: false
    freeze: true
    eval: true
    cache: true
nocite: |
    @allaire_quarto_2022, @arel-bundock_marginaleffects_2022, @wickham_ggplot2_2016, @leeuw_jspsych_2015, @burkner_brms_2017
---

@@

# Load cleaned data
list_df <- list()
list_df[["cleaned"]] <- read.csv(
  file = "../../data/clean/cleaned_pavlovia.csv"
)
# Load fitted models
  #* Pre-test
load(
    file="../../data/models/prr/pre-test/pre-test_party_model.RDS"
  )
  #* Main studies
load("../../data/temp/models/study_1_fitted.RData")
# Load data for study 2
df_study_2 <- read.csv("../../data/clean/study_2.csv") |>
  as.data.table()
  #* convert state_district and year variables  to factors
df_study_2 <- df_study_2[
  , year := tstrsplit(year, "-", keep = 1)
][
  , year := as.numeric(year)
][
  , state_district := factor(state_district)
][
  , blue_prop := blue_percent / 100
][
  , red_prop := red_percent / 100
]
```

@@

- Motivation of the project
- A snap-judgment model of politically-relevant information processing
- An experiment
- Is the world consistent with the snap-judgement model?
- The broader book project
- Q&A

### Yard signs are simple, yet effective forms of information

@@

### Pre-test: Perceptions of candidate's party affiliation depends on the color of the yard sign

@@

### Colors can convey identity

@@

## How are colors used in politics?

@@

# What do we know so far about how we process political information?

### Evaluation of political information happens automatically, and in a motivated manner

![[@zaller_simple_1992]](../../assets/slides/imgs/zaller_feldman.png){.absolute right=100 top=0}
![[@zaller_nature_1992]](../../assets/slides/imgs/zaller.jpg){.absolute right=100 bottom=0}
![[@lodge_rationalizing_2013]](../../assets/slides/imgs/lodge_taber.jpg){.absolute left=100 top=0}
![[@taber_illusion_2016]](../../assets/slides/imgs/taber_lodge_2016.png){.absolute left=100 bottom=0}

@@

## A snap-judgment model of **visual** political information processing

@@

```{mermaid}
%%| label: fig-snap-judgment-model
%%| fig-cap: Overview of model

flowchart TD;
A[Detection of color] --> B[Activation of associated memories]
B --> C[Negative Valence]
B --> D[Positive Valence]
C -.-> E[Policy stance]
D -.-> F[Policy stance]
E -.-> G[Negative Valence]
E -.-> H[Positive Valence]
F -.-> I[Negative Valence]
F -.-> J[Positive Valence]
```

- Implications
  - Refines existing info. processing models to consider pre-conscious influences.
  - Outlines the cognitive processes undergirding how we:
    - have made associations between the colors red and blue with the two parties.
    - form attitudes and behaviors based on less substantive information (e.g., policy stances).

- <span style="color: #616A6B">Motivation of the project</span>
- <span style="color: #616A6B">A snap-judgment model of politically-relevant information processing</span>
- An experiment
- Is the world consistent with the snap-judgement model?
- The broader book project
- Q&A

@@

- Do we associate the color red with Republicans and the color blue with Democrats?
- Do these associations provide information that the public act on in politics?

@@

#### Background information

@@

- Recruited 1,000 participants from Prolific
- Counterbalance treatment and background information ($\frac{1}{2}$ see treatment first; other $\frac{1}{2}$ see background questions first)
- Within each trial, participants have $\frac{1}{3}$ chance of seeing any given yard sign.
- MouseView.js [@anwyl-irvine_mouseviewjs_2022]

@@

### Do people make these associations?

@@

```{r}
#| label: fig-h-2-predictions-1
#| fig-cap: Red yard signs = Republican candidate
red <- predicted_prob_bar(
  fitted_model = list_fitted[["h_2"]][["red_multinomial"]]
  , x_axis = "trial_1_red_stimuli"
)
red
```

@@

```{r}
#| label: fig-h-2-predictions-2
#| fig-cap: Blue yard signs = Democratic candidate
blue <- predicted_prob_bar(
  fitted_model = list_fitted[["h_2"]][["blue_multinomial"]]
  , x_axis = "trial_1_blue_stimuli"
  , treatment = "Blue"
)
blue
```

### What does conflicting colors do to these associations?

@@

```{r}
#| label: fig-h-2a-predictions
#| layout-nrow: 2
#| fig-cap: Mixing red and blue in a yard sign increases uncertainty about partisanship
#| fig-subcap:
#|   - Trial 2 Red treatment
#|   - Trial 2 Blue treatment
#|   - Trial 3 Red treatment
#|   - Trial 3 Blue treatment
plot_trial_2_red <- predicted_prob_bar(
  fitted_model = list_fitted[["h_2a"]][["trial_2_red_multinomial"]]
  , x_axis = "trial_2_red_stimuli"
)
plot_trial_2_blue <- predicted_prob_bar(
  fitted_model = list_fitted[["h_2a"]][["trial_2_blue_multinomial"]]
  , x_axis = "trial_2_blue_stimuli"
  , treatment = "Blue"
)
plot_trial_3_red <- predicted_prob_bar(
  fitted_model = list_fitted[["h_2a"]][["trial_3_red_multinomial"]]
  , x_axis = "trial_3_red_stimuli"
)
plot_trial_3_blue <- predicted_prob_bar(
  fitted_model = list_fitted[["h_2a"]][["trial_3_blue_multinomial"]]
  , x_axis = "trial_3_blue_stimuli"
  , treatment = "Blue"
)
plot_trial_2_red
plot_trial_2_blue
plot_trial_3_red
plot_trial_3_blue
```

### Do these associations inform important political behavior?

@@

```{r}
#| label: fig-h-3-predictions-1
#| fig-cap: Republicans are more likely to vote for candidate with red yard sign, Democrats less likely
red <- predicted_prob_bar(
  fitted_model = list_fitted[["h_3"]][["red"]]
  , x_axis = "trial_1_red_stimuli"
  , treatment = "Red"
  , hypothesis = "H3"
  , x_label = "Party ID"
  , y_label = "Pr(Vote for candidate)"
  , legend_title = "Treatment"
)

```{r}
#| label: fig-h-3-predictions-2
#| fig-cap: Democrats are more likely to vote for candidate with blue yard signs, Republicans less likely
blue <- predicted_prob_bar(
  fitted_model = list_fitted[["h_3"]][["blue"]]
  , x_axis = "trial_1_blue_stimuli"
  , treatment = "Blue"
  , hypothesis = "H3"
  , x_label = "Party ID"
  , y_label = "Pr(Vote for candidate)"
  , legend_title = "Treatment"
)

## Study 2

### Do practitioners think of color when designing yard signs?

> There obviously is a strong association with blue and the Democratic Party and red and the Republican Party. We've seen in some of our testing that specifically MAGA red tends to elicit a slightly stronger association with Republicans/conservatives/Trump than other shades.
---

### Campaigns use the colors more or less red and blue depending on partisan composition of electoral district

#### DV: the amount of red and blue in political yard signs

@@

@@

### More blue on the yard signs in Democratic strongholds

blue <- predicted_prob_bar(
  fitted_model = list_fitted[["h_5"]][["blue"]]
  , treatment = "Blue"
  , hypothesis = "H5"
)

### More red on the yard signs in Republican strongholds

red <- predicted_prob_bar(
  fitted_model = list_fitted[["h_5"]][["red"]]
  , treatment = "Red"
  , hypothesis = "H5"
)
red
```

@@

::: {.column width="50%"}
How identity is communicated; its effects

- Party Identification (this book)
- Gender and politics
- Racial and ethnic politics
:::

::: {.column width="50%"}
Methodological

- Text as data
- Images as data
- Data munging
- Multiple imputation
:::

@@

### Study 2

@@

### List of model specifications for Study 2

- [Moderated by age](#moderated-by-age)
- [Moderated by colorblindness](#moderated-by-colorblindness)
- [Dependent on the amount of the color red and blue](#h_2a)
- [Include treatment indicator variables in the same model](#single-model)

### $H_1$

```{r}
#| label: tbl-h1-trial-1
#| tbl-cap: Average time between cursor movements (Trial 1)
df_movement_trial_1 <- list_df[["cleaned"]][
  , c(
    "trial_1_difference_Time"
    , "trial_1_stimulus"
    , "trial_1_difference_X"
    , "trial_1_difference_Y"
  )
]
setnames(
  df_movement_trial_1
  , old = c(
    "trial_1_difference_Time"
    , "trial_1_difference_X"
    , "trial_1_difference_Y"
  )
  , new = c(
    "Δ<sub>t</sub> (milliseconds)"
    , "Δ<sub>x</sub> (pixels)"
    , "Δ<sub>y</sub> (pixels)"
  )
)

@@

@@

@@

list_ppc[["h_2a"]][["trial_2_red_ordinal"]]
list_ppc[["h_2a"]][["trial_2_blue_ordinal"]]
```
---

@@

---
```{r}
#| label: fig-h-2a-ordinal-trial-3-ppc
#| fig-cap: Posterior Predictive Checks for Ordinal models testing $H_{2a}$, Trial 3
#| fig-subcap:
#|   - Red treatment
#|   - Blue treatment

>>>>

---
title: "The Shape and <span style='color: #b70000'>Co</span><span style='color: #00AEF3'>lor</span> of Politics"
author:
    - name: Damon C. Roberts [{{< fa brands orcid size=xs >}}](https://orcid.org/0000-0002-4360-3675)
format:
    simpledarkjs-revealjs:
        multiplex: true
        output-file: color-book.html
        slide-level: 5
        transition: none
        slide-number: c
bibliography: ../../../assets/candidate_support_chapter_references.bib
execute:
    echo: false
    freeze: true
    eval: true
    cache: true
nocite: |
    @allaire_quarto_2022, @arel-bundock_marginaleffects_2022, @wickham_ggplot2_2016, @leeuw_jspsych_2015, @burkner_brms_2017, @zaller_simple_1992, @zaller_nature_1992, @lodge_rationalizing_2013, @taber_illusion_2016
---

@@

# Load cleaned data
list_df <- list()
list_df[["cleaned"]] <- read.csv(
  file = "../../data/clean/cleaned_pavlovia.csv"
)
# Load fitted models
  #* Pre-test
load(
    file="../../data/models/prr/pre-test/pre-test_party_model.RDS"
  )
  #* Main studies
load("../../data/temp/models/study_1_fitted.RData")
# Load data for study 2
df_study_2 <- read.csv("../../data/clean/study_2.csv") |>
  as.data.table()
  #* convert state_district and year variables  to factors
df_study_2 <- df_study_2[
  , year := tstrsplit(year, "-", keep = 1)
][
  , year := as.numeric(year)
][
  , state_district := factor(state_district)
][
  , blue_prop := blue_percent / 100
][
  , red_prop := red_percent / 100
]

# Set default for plot color scheme

plot_color_scheme <- FALSE
```

## Available to you to follow along and view more

@@

- <span style="color: #b70000"> Motivation of the project</span>
- A snap-judgment model of politically-relevant information processing
- An experiment
- Is the world consistent with the snap-judgement model?
- The broader book project
- Q&A

## Yard signs are simple, yet effective forms of information

@@

### Pre-test: Perceptions of candidate's party affiliation depends on the <span style='color: #b70000'>co</span><span style='color: #00AEF3'>lor</span> of the yard sign

@@

### <span style='color: #b70000'>Col</span><span style='color: #00AEF3'>ors</span> can convey identity

@@

## How are <span style='color: #b70000'>col</span><span style='color: #00AEF3'>ors</span> used in politics?

@@

## What do we know so far about how we process political information?

### Political information is <span style='color: #b70000'>identity-based</span> and <span style='color: #00AEF3'>evokes affect</span>

::::: {.columns}

:::: {.column width="60%"}
::: {#fig-pip layout-ncol=2}
![](../../assets/slides/imgs/zaller.jpg){width=1.46in}
![](../../assets/slides/imgs/lodge_taber.jpg){width=1.46in}

Dominant models of political information processing
:::
::::

::::{.column width="40%"}

A key takeaway is that we are being pushed to react to information to before we even realize it.
::::

:::::

@@

## [<span style='color: #b70000'>A snap-judgment model of</span> <span style='color: #00aef3'>visual political information processing</span>](#full-snap-judgment-model)

### Visual information is primitive

- We can process it faster, and automatically
- It is ubiquitous
- It can carry a significant amount of information
    - E.g., the color <span style='color: #FFCD00'>yellow</span> has associations with bananas, with our favorite sweater, with the Iowa Hawkeys, etc.
    - We have positive and negative affect with all of these.

### So, how can it be for politics?

- These associations have been strengthened over time as the consistent usage associating Republicans and Democrats.
- Our feelings toward the object that is associated with those colors can be activated because of those colors and the association.
- Because of the centrality of vision for many living organisms, our brain is designed around this. It happens first.
    - <span style='color: #b70000'>We process and re</span><span style='color: #00aef3'>act to color first.</span>
- Given this, we are already in a state of mind. We have made a snap-judgment that can be updated with new information, but nonetheless are influenced by it.

### Implications

::: {.column width="50%"}

**Substantive Innovations**

- Presents a cognitive model that builds upon existing info. processing models to consider pre-conscious influences.
    - All of these steps happen <span style='color: #b70000'>bef</span><span style='color: #00aef3'>ore</span> the pre-existing info. processing models
:::

::: {.column width="50%"}

**Methodological Innovations**

- Using mousetracking with a survey experiment to examine pre-conscious motivations.
- Use image-based classification
:::

@@

- <span style="color: #616A6B">Motivation of the project</span>
- <span style="color: #616A6B">A snap-judgment model of politically-relevant information processing</span>
- <span style="color: #b70000">A survey experiment</span>
- Is the world consistent with the snap-judgement model?
- The broader book project
- Q&A

@@

- Do we associate the color <span style='color: #b70000'>red</span> with Republicans and the color <span style='color: #00aef3'>blue</span> with Democrats?
- Do these associations provide information that the public act on in politics?
- How do we interact with visual information?

@@

#### [Background information](#tbl-study-1-measures)

@@

- Recruited [1,000 participants](#tbl-study-1-descriptives) from an online survey experiment platform; Prolific.
- Counterbalance treatment and background information ($\frac{1}{2}$ see treatment first; other $\frac{1}{2}$ see background questions first)
- Within each trial, participants have $\frac{1}{3}$ chance of seeing any given yard sign.
- MouseView.js [@anwyl-irvine_mouseviewjs_2022]
    - Use this instead of eye-tracking.
    - Do not need to use a convenience sample of students.

@@

### A pre-registered expectation

- People associate the colors <span style='color: #b70000'>red</span> and <span style='color: #00aef3'>blue</span> with Republicans and Democrats, respectively.
  - Replicating the pre-test

#### [Red yard signs = Republican candidate](#h_2)

```{r}
#| label: fig-h-2-predictions-1
#| fig-cap: Red yard signs = Republican candidate
red <- predicted_prob_bar(
  fitted_model = list_fitted[["h_2"]][["red_multinomial"]]
  , x_axis = "trial_1_red_stimuli"
  , gray = plot_color_scheme
)
red
```

#### [<span style='color: #00aef3'>Blue yard signs = Democratic candidate</span>](#h_2)

```{r}
#| label: fig-h-2-predictions-2
#| fig-cap: Blue yard signs = Democratic candidate
blue <- predicted_prob_bar(
  fitted_model = list_fitted[["h_2"]][["blue_multinomial"]]
  , x_axis = "trial_1_blue_stimuli"
  , treatment = "Blue"
  , gray = plot_color_scheme
)
blue
```

### A pre-registered expectation

Subjects will use color as a basis for making a decision on whom they should vote for.

- Republican subjects will express preference for a candidate with a pre-dominantly <span style='color: #b70000'>red</span> yard sign.
- Democratic subjects will express preference for a candidate with a pre-dominantly <span style='color: #00aef3'>blue</span> yard sign.

#### [Republicans are more likely to vote for a candidate with a red yard sign, Democrats are less likely](#h_3)

```{r}
#| label: fig-h-3-predictions-1
#| fig-cap: Republicans are more likely to vote for candidate with red yard sign, Democrats less likely
red <- predicted_prob_bar(
  fitted_model = list_fitted[["h_3"]][["red"]]
  , x_axis = "trial_1_red_stimuli"
  , treatment = "Red"
  , hypothesis = "H3"
  , x_label = "Party ID"
  , y_label = "Pr(Vote for candidate)"
  , legend_title = "Treatment"
  , gray = plot_color_scheme
)

#### [<span style='color: #00aef3'>Democrats are more likely to vote for a candidate with a blue yard sign, Republicans less likely</span>](#h_3)

```{r}
#| label: fig-h-3-predictions-2
#| fig-cap: Democrats are more likely to vote for candidate with blue yard signs, Republicans less likely
blue <- predicted_prob_bar(
  fitted_model = list_fitted[["h_3"]][["blue"]]
  , x_axis = "trial_1_blue_stimuli"
  , treatment = "Blue"
  , hypothesis = "H3"
  , x_label = "Party ID"
  , y_label = "Pr(Vote for candidate)"
  , legend_title = "Treatment"
  , gray = plot_color_scheme
)

### A pre-registered expectation

When you include conflicting information (<span style='color: #00aef3'>blue</span> on a <span style='color: #b70000'>red</span> yard sign; <span style='color: #b70000'>red</span> on a <span style='color: #00aef3'>blue</span> yard sign), subjects will be less certain about the partisanship of the candidate

#### [Mixing red and blue in a yard sign <span style='color: #00aef3'>increases uncertainty about partisanship</span>](#h_2a)

```{r}
#| label: fig-h-2a-predictions-trial-2
#| layout-ncol: 2
#| fig-cap: Mixing red and blue in a yard sign increases uncertainty about partisanship
#| fig-subcap:
#|   - Trial 2 Red treatment
#|   - Trial 2 Blue treatment
plot_trial_2_red <- predicted_prob_bar(
  fitted_model = list_fitted[["h_2a"]][["trial_2_red_multinomial"]]
  , x_axis = "trial_2_red_stimuli"
  , gray = plot_color_scheme
)
plot_trial_2_blue <- predicted_prob_bar(
  fitted_model = list_fitted[["h_2a"]][["trial_2_blue_multinomial"]]
  , x_axis = "trial_2_blue_stimuli"
  , treatment = "Blue"
  , gray = plot_color_scheme
)
plot_trial_3_red <- predicted_prob_bar(
  fitted_model = list_fitted[["h_2a"]][["trial_3_red_multinomial"]]
  , x_axis = "trial_3_red_stimuli"
  , gray = plot_color_scheme
)
plot_trial_3_blue <- predicted_prob_bar(
  fitted_model = list_fitted[["h_2a"]][["trial_3_blue_multinomial"]]
  , x_axis = "trial_3_blue_stimuli"
  , treatment = "Blue"
  , gray = plot_color_scheme
)
plot_trial_2_red
plot_trial_2_blue
```

@@

```{r}
#| label: fig-h-2a-predictions-trial-3
#| layout-ncol: 2
#| fig-cap: Mixing red and blue in a yard sign increases uncertainty about partisanship (cont.)
#| fig-subcap:
#|   - Trial 3 Red treatment
#|   - Trial 3 Blue treatment

plot_trial_3_red
plot_trial_3_blue
```

### A pre-registered expectation

Subjects will spend more time and will move their cursor more when looking at <span style='color: #00aef3'>blue</span> and <span style='color: #b70000'>red</span> yard signs

#### When viewing a white yard sign, subjects explored the image more.

```{r}
#| label: tbl-h1-trial-1
#| tbl-cap: Average time between cursor movements (Trial 1)
df_movement_trial_1 <- list_df[["cleaned"]][
  , c(
    "trial_1_difference_Time"
    , "trial_1_stimulus"
    , "trial_1_difference_X"
    , "trial_1_difference_Y"
  )
]
setnames(
  df_movement_trial_1
  , old = c(
    "trial_1_difference_Time"
    , "trial_1_difference_X"
    , "trial_1_difference_Y"
  )
  , new = c(
    "&#x394<sub>t</sub> (milliseconds)"
    , "&#x394<sub>x</sub> (pixels)"
    , "&#x394<sub>y</sub> (pixels)"
  )
)

#### A pre-registered expectation

Subjects will take longer than they did in trial 1 to explore the yard signs when there are conflicting colors on the yard sign

#### The average subject in trial 2 explored the image more than the average participant in trial 1 for <span style='color: #b70000'>red</span> and <span style='color: #00aef3'>blue</span> yard signs

```{r}
#| label: tbl-h1-trial-2
#| tbl-cap: Average time between cursor movements (Trial 2)
df_movement_trial_2 <- list_df[["cleaned"]][
  , c(
    "trial_2_difference_Time"
    , "trial_2_stimulus"
    , "trial_2_difference_X"
    , "trial_2_difference_Y"
  )
]
setnames(
  df_movement_trial_2
  , old = c(
    "trial_2_difference_Time"
    , "trial_2_difference_X"
    , "trial_2_difference_Y"
  )
  , new = c(
    "&#x394<sub>t</sub> (milliseconds)"
    , "&#x394<sub>x</sub> (pixels)"
    , "&#x394<sub>y</sub> (pixels)"
  )
)
modelsummary::datasummary_balance(
  ~trial_2_stimulus
  , data = df_movement_trial_2
  , notes = "Data source: Prolific sample."
  , escape = FALSE
)
```

#### The average subject in trial 3 spent more time exploring the <span style='color: #b70000'>red</span> and <span style='color: #00aef3'>blue</span> yard signs than the average participant in trial 1

```{r}
#| label: tbl-h1-trial-3
#| tbl-cap: Average time between cursor movements (Trial 3)
df_movement_trial_3 <- list_df[["cleaned"]][
  , c(
    "trial_3_difference_Time"
    , "trial_3_stimulus"
    , "trial_3_difference_X"
    , "trial_3_difference_Y"
  )
]
setnames(
  df_movement_trial_3
  , old = c(
    "trial_3_difference_Time"
    , "trial_3_difference_X"
    , "trial_3_difference_Y"
  )
  , new = c(
    "&#x394<sub>t</sub> (milliseconds)"
    , "&#x394<sub>x</sub> (pixels)"
    , "&#x394<sub>y</sub> (pixels)"
  )
)

modelsummary::datasummary_balance(
  ~trial_3_stimulus
  , data = df_movement_trial_3
  , notes = "Data source: Prolific sample."
  , escape = FALSE
)
```

@@

- <span style="color: #616A6B">Motivation of the project</span>
- <span style="color: #616A6B">A snap-judgment model of politically-relevant information processing</span>
- <span style="color: #616A6B">A survey experiment</span>
- <span style="color: #b70000">Is the world consistent with the snap-judgement model?</span>
- The broader book project
- Q&A

## Study 2 - Is the world consistent with my theory?

### A pre-registered expectation

Campaigns use the colors more or less <span style='color: #b70000'>red</span> and <span style='color: #00aef3'>blue</span> depending on partisan composition of electoral district

####  Talking to practitioners

> There obviously is a strong association with blue and the Democratic Party and red and the Republican Party. We've seen in some of our testing that specifically MAGA red tends to elicit a slightly stronger association with Republicans/conservatives/Trump than other shades.

@@

@@

It remains unclear whether this is just ***one*** group of practitioners, however.

#### [<span style='color: #b70000'>D</span><span style='color: #00aef3'>V</span>: the amount of red <span style='color: #00aef3'>and blue in political yard signs</span>](#tbl-yard-sign-summary)

@@

### [<span style='color: #00aef3'>More blue on the yard signs in Democratic strongholds</span>](#h_5)

blue <- predicted_prob_bar(
  fitted_model = list_fitted[["h_5"]][["blue"]]
  , treatment = "Blue"
  , hypothesis = "H5"
  , gray = plot_color_scheme
)

### [More red on the yard signs in Republican strongholds](#h_5)

red <- predicted_prob_bar(
  fitted_model = list_fitted[["h_5"]][["red"]]
  , treatment = "Red"
  , hypothesis = "H5"
  , gray = plot_color_scheme
)
red
```

@@

- <span style="color: #616A6B">Motivation of the project</span>
- <span style="color: #616A6B">A snap-judgment model of politically-relevant information processing</span>
- <span style="color: #616A6B">A survey experiment</span>
- <span style="color: #616A6b">Is the world consistent with the snap-judgement model?</span>
- <span style="color: #b70000">The broader book project</span>
- Q&A

@@

![](../../assets/slides/imgs/roberts_gs.png)

@@

### Experiment

@@

### List of model specifications for Experiment

- [Moderated by age](#moderated-by-age)
- [Moderated by colorblindness](#moderated-by-colorblindness)
- [Dependent on the amount of the color red and blue](#h_2a)
- [Include treatment indicator variables in the same model](#single-model)
- [Multinomial (main) versus Ordered logistic regressions](#h_2)

@@

##### Posterior Predictive Check

@@

#### Multinomial Cont.

@@

list_ppc[["h_2a"]][["trial_2_red_ordinal"]]
list_ppc[["h_2a"]][["trial_2_blue_ordinal"]]
```

#### Ordered Cont.

@@

##### Posterior Predictive Check

```{r}
#| label: fig-h-2a-ordinal-trial-3-ppc
#| fig-cap: Posterior Predictive Checks for Ordinal models testing $H_{2a}$, Trial 3
#| fig-subcap:
#|   - Red treatment
#|   - Blue treatment
